Contribution of computational intelligence tools \\ in the improvement of strategy games

### 2018-02-28 article.tex
Probleme de figure résolu
Add files via upload

\begin{figure}
\begin{tikzpicture}[scale = 0.8]
\draw [fill =gray, ultra thick, gray] (2,1) circle [radius=0.3];
\node at (2,1) {14};
\draw [fill =gray, ultra thick, gray] (3,2) circle [radius=0.4];
\draw [fill = gray ,thick] (3.5,2.8) to (3.7,2.7) to (3.8,3.2) to (3.5,2.8);
\node at (3.5,2.5) {20};
\node at (3,2) {29};
\draw [fill =gray, ultra thick, gray] (4,1) circle [radius=0.3];
\node at (4,1) {45};
\draw [fill =gray ,thick] (3,1.1) to (3,0.9) to (2.7,1) to (3,1.1);
\node at (3.2,1) {12};
\draw [fill =gray, ultra thick, gray] (6,0.3) circle [radius=0.3];
\node at (6,0.3) {12};
\draw [fill =gray, ultra thick, gray] (8.5,1.5) circle [radius=0.6];
\node at (8.5,1.5) {33};
\draw [fill = gray ,thick] (7.3,1.6) to (6.9,1.5) to (7.3,1.4) to (7.3,1.6);
\node at (7.6,1.5) {10};
\draw [fill =gray, ultra thick, gray] (8,3.5) circle [radius=0.3];
\node at (8,3.5) {18};
\draw [fill =gray, ultra thick, gray] (6.5,4.5) circle [radius=0.6];
\node at (6.5,4.5) {9};
%\draw [fill =lightgray, ultra thick, lightgray] (3.5,3) circle [radius=0.3];
%\node at (3.5,3) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,1.5) circle [radius=0.6];
\node at (5.5,1.5) {136};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,3) circle [radius=0.4];
\node at (5.5,3) {67};
\draw [fill =lightgray, ultra thick, lightgray] (7,2.5) circle [radius=0.3];
\node at (7,2.5) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,7.5) circle [radius=0.6];
\node at (5.5,7.5) {102};
\draw (1,3.2) circle [radius=0.3];
\node at (1,3.2) {88};
\draw [thick] (1.1,2.5) to (1.3,2.6) to (1.3,2.2) to (1.1,2.5);
\draw [thick] (1.3,1.8) to (1.5,1.9) to (1.5,1.5) to (1.3,1.8);
\node at (1.2,2.7) {8};
\node at (1.3,2) {8};
\draw  (1,5.5) circle [radius=0.4];
\node at (1,5.5) {8};
\draw  (2.5,4.8) circle [radius=0.6];
\node at (2.5,4.8) {10};
\draw  (3.2,7) circle [radius=0.3];
\draw [thick] (3.3,5.7) to (3.7,5.9) to (3.5,5.5) to (3.3,5.7);
\draw [thick] (4.2,6.5) to (4.6,6.7) to (4.4,6.3) to (4.2,6.5);
\node at (3.1,5.4) {15};
\node at (4,6.2) {10};
\node at (3.2,7) {15};
\draw  (4.5,4) circle [radius=0.4];
\node at (4.5,4) {2};
\draw  (5.5,6) circle [radius=0.3];
\node at (5.5,6) {45};
\draw  (8,6.5) circle [radius=0.5];
\draw [thick] (8,5.5) to (8.2,5.5) to (8.1,5.1) to (8,5.5);
\draw [thick] (8,4.5) to (8.2,4.5) to (8.1,4.1) to (8,4.5);
\node at (8,6.5) {1};
\node at (8.1,5.7) {2};
\node at (8.1,4.7) {8};
\end{tikzpicture}
\caption{Simulated of an early stage of a run in Planet Wars. White planets belongs to the player (blue color in the game), dark grey belong to the opponent (red in the game), and light grey planets belong to no player. The triangles are fleets, and the numbers (in planets and triangles) represent the
starships.}
\end{figure}

@@

\begin{figure}
\begin{tabular}{c}
\includegraphics[scale = 0.8]{clonaS}
\end{tabular}
\caption{Clonal selection mechanism}
\end{figure}

@@

@@

\caption{AIS diagram}

@@

\section{AisBot: the Canquer Bot}
In the previous sections, we explained that there are two primary constraints in the development of the bot's behaviours. The main constraint is the limited time available for the bot to move (1 second). The second fundamental constraint that is no information could be stored from the previous turns. Based on these two major restrictions, the design performance and the implementation possibilities are limited. However, some researchers have been carried out on the memory solutions based on metaheuristic algorithms to make the bot store some information from its previous actions to determine the next move, but most of them are limited by the time factor; the performance of an EA is limited by time, is almost impossible to run an EA in each step of time (1 second). For the bot's behaviour evaluation it is no possible to improve an action without any feedback from one turn to the next. \\
The purpose of this investigation is to obtain data which will help to address those research restrictions, while these data were collected using a set of rules in order to optimize the bot's behaviour. \\
Anyway, in this case of study, we have to perform a single action mode: send starships from a planet to another; to make fleets move in the map, the bot should distinguish between self-planets and the enemy's planets. Based on this simple action, one of the greatest challenges is to determine which planet that will generate the fleets, how many starships will include on it and what is the planet will be targeted. In the next, we will describe our bot's behaviour, following the definition of the parameters used in the optimization. Finally, we will explain the technics governing the bot.

@@

\includepdf[scale=0.7,pages=1]{botDiagram}

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
 & $Tith_perc$ & $Tith_prob$ & $W_NS$ & $W_GR$ & $W_DIS$ & $Pool_perc$ & $Support_perc$ & $Support_prob$ \\ 
 \hline
 Before & 0.959 & 0.651 & 0.665 & 0.122 & 0.785 & 0.113 & 0.64 & 0.366 \\  
 \hline
 After & 0.057 & 0.845 & 0.447 & 0.323 & 0.124 & 0.814 & 0.636 & 0.32 \\
 \hline  
\end{tabular}
\caption{Parameters used in the CLONALG algorithm}
\label{TABLE 2}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 Maps & 5 & 10 & 20 & 50 & 100 \\ 
 \hline
 Before & 135 & 128 & 161 & 102 & 144 \\  
 \hline
 After & 98 & 80 & 70 & 72 & 87 \\
 \hline  
\end{tabular}
\caption{results after 5 games of our AisBot with random parameters and after the optimization against the RandomBot}
\label{TABLE 3}
\end{table}

@@

\section{conclusions}

>>>>

\begin{figure}
\begin{tikzpicture}[scale = 0.8]
\draw [fill =gray, ultra thick, gray] (2,1) circle [radius=0.3];
\node at (2,1) {14};
\draw [fill =gray, ultra thick, gray] (3,2) circle [radius=0.4];
\draw [fill = gray ,thick] (3.5,2.8) to (3.7,2.7) to (3.8,3.2) to (3.5,2.8);
\node at (3.5,2.5) {20};
\node at (3,2) {29};
\draw [fill =gray, ultra thick, gray] (4,1) circle [radius=0.3];
\node at (4,1) {45};
\draw [fill =gray ,thick] (3,1.1) to (3,0.9) to (2.7,1) to (3,1.1);
\node at (3.2,1) {12};
\draw [fill =gray, ultra thick, gray] (6,0.3) circle [radius=0.3];
\node at (6,0.3) {12};
\draw [fill =gray, ultra thick, gray] (8.5,1.5) circle [radius=0.6];
\node at (8.5,1.5) {33};
\draw [fill = gray ,thick] (7.3,1.6) to (6.9,1.5) to (7.3,1.4) to (7.3,1.6);
\node at (7.6,1.5) {10};
\draw [fill =gray, ultra thick, gray] (8,3.5) circle [radius=0.3];
\node at (8,3.5) {18};
\draw [fill =gray, ultra thick, gray] (6.5,4.5) circle [radius=0.6];
\node at (6.5,4.5) {9};
%\draw [fill =lightgray, ultra thick, lightgray] (3.5,3) circle [radius=0.3];
%\node at (3.5,3) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,1.5) circle [radius=0.6];
\node at (5.5,1.5) {136};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,3) circle [radius=0.4];
\node at (5.5,3) {67};
\draw [fill =lightgray, ultra thick, lightgray] (7,2.5) circle [radius=0.3];
\node at (7,2.5) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,7.5) circle [radius=0.6];
\node at (5.5,7.5) {102};
\draw (1,3.2) circle [radius=0.3];
\node at (1,3.2) {88};
\draw [thick] (1.1,2.5) to (1.3,2.6) to (1.3,2.2) to (1.1,2.5);
\draw [thick] (1.3,1.8) to (1.5,1.9) to (1.5,1.5) to (1.3,1.8);
\node at (1.2,2.7) {8};
\node at (1.3,2) {8};
\draw  (1,5.5) circle [radius=0.4];
\node at (1,5.5) {8};
\draw  (2.5,4.8) circle [radius=0.6];
\node at (2.5,4.8) {10};
\draw  (3.2,7) circle [radius=0.3];
\draw [thick] (3.3,5.7) to (3.7,5.9) to (3.5,5.5) to (3.3,5.7);
\draw [thick] (4.2,6.5) to (4.6,6.7) to (4.4,6.3) to (4.2,6.5);
\node at (3.1,5.4) {15};
\node at (4,6.2) {10};
\node at (3.2,7) {15};
\draw  (4.5,4) circle [radius=0.4];
\node at (4.5,4) {2};
\draw  (5.5,6) circle [radius=0.3];
\node at (5.5,6) {45};
\draw  (8,6.5) circle [radius=0.5];
\draw [thick] (8,5.5) to (8.2,5.5) to (8.1,5.1) to (8,5.5);
\draw [thick] (8,4.5) to (8.2,4.5) to (8.1,4.1) to (8,4.5);
\node at (8,6.5) {1};
\node at (8.1,5.7) {2};
\node at (8.1,4.7) {8};
\end{tikzpicture}
\caption{an early stage of a planet wars game, as shown here there are planet categories, the darker grey (red in the game) ones related to the player, the white ones (green in the game) related to the opponent and the neutral planets are coloured by light grey. Fleets presented by triangles and the numbers are the starships included on them.}
\end{figure}

@@

\begin{figure}
\begin{tabular}{c}
\includegraphics[scale = 0.8]{clonaS}
\end{tabular}
\caption{The biological clonal selection mechanism and its steps in order to defend the body, starting by detecting of the antigen until removing it.}
\end{figure}

@@

\centering

@@

\caption{The diagram showed the ordered steps for running an AIS algorithm based on clonal selection algorithm (CLONALG) }

@@

\section{AisBot: the Canquer Bot}

In the previous sections, we explained that there are two primary constraints in the development of the bot's behaviours. The main constraint is the limited time available for the bot to move (1 second). The second fundamental constraint that is no information could be stored from the previous turns. Based on these two major restrictions, the design performance and the implementation possibilities are limited. However, some researchers have been carried out on the memory solutions based on metaheuristic algorithms to make the bot store some information from its previous actions to determine the next move, but most of them are limited by the time factor; the performance of an EA is limited by time, is almost impossible to run an EA in each step of time (1 second). For the bot's behaviour evaluation it is no possible to improve an action without any feedback from one turn to the next. \\
The purpose of this investigation is to obtain data which will help to address those research restrictions, while these data were collected using a set of rules in order to optimize the bot's behaviour. \\
Anyway, in this case of study, we have to perform a single action mode: send starships from a planet to another; to make fleets move in the map, the bot should distinguish between self-planets and the enemy's planets. Based on this simple action, one of the greatest challenges is to determine which planet that will generate the fleets, how many starships will include on it and what is the planet will be targeted. In the next, we will describe our bot's behaviour, following the definition of the parameters used in the optimization. Finally, we will explain the technics governing the bot.

@@

\begin{figure*}
\centering
\draw [->][ultra thick](-1,20) -- (3,20);
\draw [->][ultra thick](-1,20) -- (2.8,20);
\node at (1,20.3) {State of game map};
\draw (3,20.5) --(3,19.5);
\draw (3,20.5) --(6,20.5);
\draw (6,20.5) --(6,19.5);
\draw (6,19.5) --(3,19.5);
\draw [->][ultra thick](6,20) -- (8,20);
\node at (4.4,20.3) {\small locate the bot's};
\node at (4.4,19.8) {\small best planet: base};
\draw (8,20.5) --(8,19.5);
\draw (8,20.5) --(13,20.5);
\draw (13,20.5) --(13,19.5);
\draw (13,19.5) --(8,19.5);
\draw [->][thick](9.2,21.8) -- (9.2,20.5);
\draw [->][thick](10.5,21.4) -- (10.5,20.5);
\draw [->][thick](11.8,21) -- (11.8,20.5);
\node at (10,20.3) {\small locate the best};
\node at (9.2,22) {\small P\_NS};
\node at (10.5,21.6) {\small P\_GR};
\node at (11.8,21.2) {\small P\_DIS};
\node at (10.5,19.8) {\small ennemy planet to attack: target};
\draw [->][ultra thick](13,20) -- (14,20);
\draw (14,20.5) --(14,19.5);
\draw (14,20.5) --(16.5,20.5);
\draw (16.5,20.5) --(16.5,19.5);
\draw (16.5,19.5) --(14,19.5);
\node at (15.3,20.3) {\small for next};
\node at (15.3,19.8) {\small colony};
\draw [->][ultra thick](15.5,19.5) -- (15.5,18.5);
\draw (15.5,18.5) --(14.5,18);
\draw (14.5,18) --(15.5,17.5);
\draw (15.5,17.5) --(16.5,18);
\draw (16.5,18) --(15.5,18.5);
\draw [->][thick](17.2,18) -- (16.5,18);
\node at (17.7,18) {\small P\_tith};
\draw [->][thick](17.2,15.5) -- (16.5,15.5);
\node at (17.7,15.5) {\small P\_tith};
\node at (15.5,18) {\small tith ?};
\node at (15.5,15.7) {\small extra};
\node at (15.5,15.4) {\small attack};
\draw [->][ultra thick](15.5,17.5) -- (15.5,16);
\node at (15.9,17.2) {\small No};
\draw (15.5,16) --(14.5,15.5);
\draw (14.5,15.5) --(15.5,15);
\draw (15.5,15) --(16.5,15.5);
\draw (16.5,15.5) --(15.5,16);
\draw [->][ultra thick](14.5,18) -- (13,18);
\node at (13.3,18.3) {\small Yes};
\draw [ultra thick](15.5,15) -- (15.5,14);
\node at (15.9,14.8) {\small No};
\draw [ultra thick](15.5,14) -- (5,14);
\draw [->][ultra thick](5,14) -- (5,17);
\draw (13,18.5) --(13,17.5);
\draw (13,17.5) --(10,17.5);
\draw (10,17.5) --(10,18.5);
\draw (10,18.5) --(13,18.5);
\node at (13.3,15.8) {\small Yes};
\node at (11.3,18.2) {\small tith from};
\node at (11.4,17.8) {\small colonie to base};
\node at (8.7,17.5) {\small tith};
\draw [->][thick](9,17.5) -- (10,17.5);
\draw [->][ultra thick](14.5,15.5) -- (13,15.5);
\node at (9.3,15.8) {\small Yes};
\draw (13,15.5) --(11.5,16.5);
\draw (11.5,16.5) --(10,15.5);
\draw (10,15.5) --(11.5,14.5);
\draw (11.5,14.5) --(13,15.5);
\node at (11.5,15.7) {\small colony near};
\node at (11.5,15.2) {\small to target};
\draw [->][ultra thick](10,15.5) -- (9,15.5);
\draw (9,16.3) --(9,14.8);
\draw (9,14.8) --(6,14.8);
\draw (6,14.8) --(6,16.3);
\draw (6,16.3) --(9,16.3);
\node at (7.5,15.7) {\small extra attack from};
\node at (7.5,15.3) {\small colony to base};
\draw [->][thick](7.5,16.6) -- (7.5,16.3);
\node at (7.7,16.8) {\small extra\_attack};
\draw [->][ultra thick](10,18) -- (6,18);
\draw (6,18) --(5,19);
\draw (5,19) --(4,18);
\draw (4,18) --(5,17);
\draw (5,17) --(6,18);
\node at (5,18.2) {\small Last};
\node at (5.1,17.8) {\small colony ?};
\draw [->][ultra thick](5.7,18.3) -- (14,19.5);
\node at (5.9,18.5) {\small No};
\node at (3.7,18.3) {\small Yes};
\draw (6,15.5) -- (5.7,15.5);
\draw [->][ultra thick](5.7,15.5) -- (5.7,17.7);
\draw [->][ultra thick](4,18) -- (2,18);
\draw (2,18) -- (0.5,19.5);
\draw (0.5,19.5) -- (-1,18);
\draw (-1,18) -- (0.5,16.5);
\draw (0.5,16.5) -- (2,18);
\node at (0.5,18.5) {\small Expansion };
\node at (0.5,18) {\small or };
\node at (0.5,17.5) {\small conquest ?};
\draw [ultra thick](1,17) -- (1,15.5);
\draw [ultra thick](1,15.5) -- (2.5,15.5);
\node at (1.8,15.7) {\small conquest};
\draw [->][ultra thick](2.5,15.5) -- (2.5,14.8);
\draw (1,14.8) -- (4,14.8);
\draw (4,14.8) -- (4,13.5);
\draw (4,13.5) -- (1,13.5);
\draw (1,13.5) -- (1,14.8);
\node at (2.5,14.3) {\small calculate needed};
\node at (2.5,13.9) {\small fleets to win};
\draw [ultra thick](0,17) -- (0,15.5);
\draw [ultra thick](0,15.5) -- (-1.5,15.5);
\draw [->][ultra thick](-1.5,15.5) -- (-1.5,11);
\draw (-2.5,11) -- (1,11);
\draw (-2.5,9.5) -- (1,9.5);
\draw (-2.5,11) -- (-2.5,9.5);
\draw (1,11) -- (1,9.5);
\draw [ultra thick](2.5,13.5) -- (2.5,12);
\draw [ultra thick](2.5,12) -- (0.5,12);
\node at (-0.8,15.7) {\small expansion};
\draw [->][ultra thick](0.5,12) -- (0.5,11);
\node at (-0.8,10.4) {\small sent fleets};
\node at (-0.8,10) {\small to target palnet};
\draw [->][ultra thick](1,10.3) -- (4.8,10.3);
\draw [->][ultra thick](1,10.3) -- (5,10.3);
\node at (3,10.5) {\small Next moves of fleets};
\draw [->][thick](2,9.6) -- (1,9.6);
\node at (2.9,9.6) {\small extra\_attack};
\caption{The states that are governing the behaviour of the AisBot including the parameters used on the evaluation of the bot's behaviour. these parameters will improve by the clonal selection algorithm (CLONALG).}
\end{figure*}

%%\includepdf[scale=0.7,pages=1]{botDiagram}

@@

\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
 & $Tith_perc$ & $Tith_prob$ & $W_NS$ & $W_GR$ & $W_DIS$ & $Pool_perc$ & $Support_perc$ & $Support_prob$ \\ 
 \hline
 Before & 0.959 & 0.651 & 0.665 & 0.122 & 0.785 & 0.113 & 0.64 & 0.366 \\  
 \hline
 After & 0.057 & 0.845 & 0.447 & 0.323 & 0.124 & 0.814 & 0.636 & 0.32 \\
 \hline  
\end{tabular}
\caption{Parameters used in the CLONALG algorithm}
\label{TABLE 2}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 Maps & 5 & 10 & 20 & 50 & 100 \\ 
 \hline
 Before & 135 & 128 & 161 & 102 & 144 \\  
 \hline
 After & 98 & 80 & 70 & 72 & 87 \\
 \hline  
\end{tabular}
\caption{results after 5 games of our AisBot with random parameters and after the optimization against the RandomBot}
\label{TABLE 3}
\end{table*}

@@

\section{conclusions}
The planet wars game it was classified as an RTS game, where the player (bots) fight against others in real-time. The main aim of this study is to investigate the application of the Evolutionary Algorithms (EAs) and the better results can be obtained in real-world problems, by tunning real game scenarios that used a parametrise behaviour of a bot tuning by an AIS Algorithm. This problem showed that the EAs can improve the evaluation of a hand-coded bot by defeating multiple opponents in different situations in fewer turns. In the other hand, the high capabilities of an evolutionary approach can be improved at least in this type of problems.
